### 2021-06-05 paper/report.tex
update figures.

At the core of our agent-based model are physical contacts between heterogeneous agents (Figure~\ref{fig:broad_model_description}).\footnote{We provide a detailed comparison to other approaches in \ref{sec:literature_review}. The model most closely related to ours is described in \citet{Hinch2020}.} Each contact between an infectious indvidual and somebody susceptible to the disease bears the risk of transmitting the virus. Contacts occur in the household, at work, at school, or in other settings (leisure activities, grocery shopping, medical appointments, etc.).\comment[id=HM]{Systemic relevance of work?} Some contacts recur regularly, others occur at random. Random contacts are typically assortative in age and geographical location. Empirical applications can take the population structure from census data and the types and frequency of contacts from diary data measuring contacts before the pandemic \citep[e.g.][]{Mossong2008}.\comment[id=HM]{cite other stuff, too?} The dimensions are chosen so that the most common NPIs can be modelled in great detail by reducing the number of contacts in a particular setting or the risk of transmitting the disease for a type of contact. For example, a mandate to work from home will reduce the number of work contacts to zero for a fraction of the working population. Schools and daycare can be closed entirely, operate at reduced capacity including an alternating schedule, or implement mitigation measures like masking requirements or air filters.\comment[id=HM]{cite \url{https://science.sciencemag.org/content/early/2021/04/28/science.abh2939}} Curfews may reduce the number of contacts in non-work/non-school settings. In any setting, measures like masking requirements would reduce the probability of infection associated with a contact.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model-graph-top-left}
        \caption{{\small Model description}}
        \label{fig:broad_model_description}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model-graph-top-right}
        \caption{Disease progression}
        \label{fig:disease_progression}
    \end{subfigure}

@@

    \caption{Model description}
\end{figure}

@@

Figure~{fig:pandemic_drivers_model_fit} describes the evolution of the pandemic and of its drivers. The black line in Figure~\ref{fig:aggregated_fit} shows officially recorded cases; the \replaced[id=HM]{color}{blue?} line in Figure~\ref{fig:stringency_index} the Oxford Response Stringency Index\cite{Hale2020}, which tracks the tightness of non-pharmaceutical interventions. We transform the index so that lower values represent higher levels of restrictions. A value of zero means all measures incorporated in the index are turned on. The value 1 represents the situation of mid-September, where half of all restrictions incorporated in the index are active.\comment[id=HM]{Need to find version of index with a couple of measures, probably need the API access...}. In the six weeks between mid September and mid October, cases increased by a factor of \replaced[id=HM]{X}{10? Do we have RKI numbers as table somewhere?}. Restrictions were somewhat tightened in mid-October and again in early November. New infections remained constant throughout November, before rising again in December. In mid December, other lockdown. So far, traditional measures only

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        % \includegraphics[width=\textwidth]{../figures/disease_progression.png}

        Shapley values

@@

        \caption{Decomposition of effects for Figure~\ref{fig:full_newly_infected_cropped}}
        \label{fig:decompisition total cases}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

>>>>

At the core of our agent-based model are physical contacts between heterogeneous agents (Figure~\ref{fig:broad_model_description}).\footnote{We provide a detailed comparison to other approaches in \ref{sec:literature_review}. The model most closely related to ours is described in \citet{Hinch2020}.} Each contact between an infectious individual and somebody susceptible to the disease bears the risk of transmitting the virus. Contacts occur in the household, at work, at school, or in other settings (leisure activities, grocery shopping, medical appointments, etc.).\comment[id=HM]{Systemic relevance of work?} Some contacts recur regularly, others occur at random. Random contacts are typically assortative in age and geographical location. Empirical applications can take the population structure from census data and the types and frequency of contacts from diary data measuring contacts before the pandemic \citep[e.g.][]{Mossong2008}.\footnote{\citet{Hoang2019} provide access to multiple data sets on contact types and frequencies at \url{http://www.socialcontactdata.org/} covering countries from all continents except North America and Australia.} The dimensions are chosen so that the most common NPIs can be modeled in great detail by reducing the number of contacts in a particular setting or the risk of transmitting the disease for a type of contact. For example, a mandate to work from home will reduce the number of work contacts to zero for a fraction of the working population. Schools and daycare can be closed entirely, operate at reduced capacity including an alternating schedule, or implement mitigation measures like masking requirements or air filters.\comment[id=HM]{cite \url{https://science.sciencemag.org/content/early/2021/04/28/science.abh2939}} Curfews may reduce the number of contacts in non-work/non-school settings. In any setting, measures like masking requirements would reduce the probability of infection associated with a contact.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model-graph-top-left}
        \caption{{\small Model description}}
        \label{fig:broad_model_description}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model-graph-top-right}
        \caption{Disease progression}
        \label{fig:disease_progression}
    \end{subfigure}
    \vskip3ex
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

@@

    \caption{Model description}
    \label{fig:model-description}
\end{figure}

@@

Figure~\ref{fig:pandemic_drivers_model_fit} describes the evolution of the pandemic and of its drivers. The black line in Figure~\ref{fig:aggregated_fit} shows officially recorded cases; the \replaced[id=HM]{color}{blue?} line in Figure~\ref{fig:stringency_index} the Oxford Response Stringency Index\cite{Hale2020}, which tracks the tightness of non-pharmaceutical interventions. We transform the index so that lower values represent higher levels of restrictions. A value of zero means all measures incorporated in the index are turned on. The value 1 represents the situation of mid-September, where half of all restrictions incorporated in the index are active.\comment[id=HM]{Need to find version of index with a couple of measures, probably need the API access...}. In the six weeks between mid September and mid October, cases increased by a factor of \replaced[id=HM]{X}{10? Do we have RKI numbers as table somewhere?}. Restrictions were somewhat tightened in mid-October and again in early November. New infections remained constant throughout November, before rising again in December. In mid December, other lockdown. So far, traditional measures only

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/full_decomposition}

@@

        \caption{
            Decomposition of effects for Figure~\ref{fig:full_newly_infected_cropped}.

            The decomposition is based on Shapley values where the individual
            contribution of an intervention is its average contribution over different
            sizes of coalitions (combinations with other interventions). The individual
            contribution to a coalition is the difference between the effect size of the
            coalition with the particular intervention and without.
        }
        \label{fig:decompisition total cases}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
